---
title: "Final_xl2836"
author: "Xinyi Lin"
date: "11/17/2018"
output: html_document
---

```{r}
library(tidyverse)
```

# Import and tidy data

First, we should have a roughly understanding about this data.

```{r}
#mentalhealth_2014_df = read_csv("./data/mental_health_in_tech_2014.csv") 
mentalhealth_2016_df = read_csv("./data/mental_health_in_tech_2016.csv") 
```

Variables name in this data set are questions, we change it to short words for easy-reading.

• Self_employed: Are you self-employed?

• Num_employees: How many employees does your company or organization have?

• Tech_company: Is your employer primarily a tech company/organization?

• Tech_role: Is your primary role within your company related to tech/IT?

• Benefits: Does your employer provide mental health benefits as part of healthcare coverage?

• Care_options: Do you know the options for mental health care available under your employer-provided coverage?

• Employer_discussion: Has your employer ever formally discussed mental health (for example, as part of a wellness campaign or other official communication)?

• Employer_help: Does your employer offer resources to learn more about mental health concerns and options for seeking help?

• Anonymity: Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources provided by your employer?

• Medical_leave: If a mental health issue prompted you to request a medical leave from work, asking for that leave would be:

• Mental_health_consequences: Do you think that discussing a mental health disorder with your employer would have negative consequences?

• Physical_health_consequences: Do you think that discussing a physical health issue with your employer would have negative consequences?

• Coworkers_discussion: Would you feel comfortable discussing a mental health disorder with your coworkers?

• Supervisor_discussion: Would you feel comfortable discussing a mental health disorder with your direct supervisor(s)?

• Mental_vs_physical: Do you feel that your employer takes mental health as seriously as physical health?

• Obs_consequence: Have you heard of or observed negative consequences for coworkers with mental health conditions in your workplace?

• Medical_coverage: Do you have medical coverage (private insurance or state-provided) which includes treatment of mental health issues?

• Help_resourcces: Do you know local or online resources to seek help for a mental health disorder?

• Whether_reveal_business_contacts:  If you have been diagnosed or treated for a mental health disorder, do you ever reveal this to clients or business contacts?

• Reveal_concequences_business_contects: If you have revealed a mental health issue to a client or business contact, do you believe this has impacted you negatively?

• Whether_reveal_coworkers: If you have been diagnosed or treated for a mental health disorder, do you ever reveal this to coworkers or employees?

• Reveal_concequences_coworkers: If you have revealed a mental health issue to a coworker or employee, do you believe this has impacted you negatively?

• Productivity_affect: Do you believe your productivity is ever affected by a mental health issue?

• Work_time_affected: If yes, what percentage of your work time (time performing primary or secondary job functions) is affected by a mental health issue?

• Preemployers: Do you have previous employers?

• Preemployers_benefits:Have your previous employers provided mental health benefits?

• Preemployers_care_options: Were you aware of the options for mental health care provided by your previous employers?

• Preemployers_discussion: Did your previous employers ever formally discuss mental health (as part of a wellness campaign or other official communication)?

• Preemployer_help: Did your previous employers provide resources to learn more about mental health issues and how to seek help?

• Pre_anonymity: Was your anonymity protected if you chose to take advantage of mental health or substance abuse treatment resources with previous employers?

• Pre_mental_health_consequences: Do you think that discussing a mental health disorder with previous employers would have negative consequences?

• Pre_physical_health_consequences: Do you think that discussing a physical health issue with previous employers would have negative consequences?

• Pre_coworkers_discussion:Would you have been willing to discuss a mental health issue with your previous co-workers?

• Pre_supervisors_discussion: Would you have been willing to discuss a mental health issue with your direct supervisor(s)?

• Pre_mental_vs_physicalDid you feel that your previous employers took mental health as seriously as physical health?

• Pre_obs_consequenceDid you hear of or observe negative consequences for co-workers with mental health issues in your previous workplaces?

• Physical_health_interview: Would you be willing to bring up a physical health issue with a potential employer in an interview?

• Physical_health_interview_reason: Why or why not?

• Mental_health_interview: Would you bring up a mental health issue with a potential employer in an interview?

• Mental_health_interview_reason: Why or why not?

• Career_influence: Do you feel that being identified as a person with a mental health issue would hurt your career?

• Coworkers_view: Do you think that team members/co-workers would view you more negatively if they knew you suffered from a mental health issue?

• Friends_family_share: How willing would you be to share with friends and family that you have a mental illness?

• Unsupportive_badly_handled: Have you observed or experienced an unsupportive or badly handled response to a mental health issue in your current or previous workplace?

• Less_likely_reveal: Have your observations of how another individual who discussed a mental health disorder made you less likely to reveal a mental health issue yourself in your current workplace?

• Family_history: Do you have a family history of mental illness?

• Mental_health_previous: Have you had a mental health disorder in the past?

• Mental_health_now:Do you currently have a mental health disorder?

• Condition_diagnosed: If yes, what condition(s) have you been diagnosed with?

• Possible_condition: If maybe, what condition(s) do you believe you have?

• Professional_diagnosed: Have you been diagnosed with a mental health condition by a medical professional?

• Condition_professional_diagnosedIf so, what condition(s) were you diagnosed with?

• Seek_treatment: Have you ever sought treatment for a mental health issue from a mental health professional?

• Work_interferes_treated: If you have a mental health issue, do you feel that it interferes with your work when being treated effectively?

• Work_interferes_untreated:If you have a mental health issue, do you feel that it interferes with your work when NOT being treated effectively?

• Age: What is your age?

• Gender: What is your gender?

• Country_live: What country do you live in?

• Territory_live: What US state or territory do you live in?

• Country_work: What country do you work in?

• Territory_work: What US state or territory do you work in?

• Work_position: Which of the following best describes your work position?

• Work_remotely: Do you work remotely?

```{r}
colnames(mentalhealth_2016_df) <- c("self_employed", "num_employees", "tech_company", "tech_role", "benefits", "care_options", "employer_discussion", "employer_help", "anonymity", "medical_leave", "mental_health_consequences", "physical_health_consequences", "coworkers_discussion", "supervisor_discussion", "mental_vs_physical", "obs_consequence", "medical_coverage", "help_resourcces", "whether_reveal_business_contacts", "reveal_concequences_business_contects", "whether_reveal_coworkers", "reveal_concequences_coworkers", "productivity_affect", "work_time_affected", "preemployers", "preemployers_benefits", "preemployers_care_options", "preemployers_discussion", "preemployer_help", "pre_anonymity", "pre_mental_health_consequences", "pre_physical_health_consequences", "pre_coworkers_discussion", "pre_supervisors_discussion", "pre_mental_vs_physical", "pre_obs_consequence", "physical_health_interview", "physical_health_interview_reason", "mental_health_interview", "mental_health_interview_reason", "career_influence", "coworkers_view", "friends_family_share", "unsupportive_badly_handled", "less_likely_reveal", "family_history", "mental_health_previous", "mental_health_now", "condition_diagnosed", "possible_condition", "professional_diagnosed", "condition_professional_diagnosed", "seek_treatment", "work_interferes_treated", "work_interferes_untreated", "age", "gender", "country_live", "territory_live", "country_work", "territory_work", "work_position_kind", "work_remotely")
```

```{r}
summary(as.factor(mentalhealth_2016_df$gender))
summary(as.factor(mentalhealth_2016_df$country_work))
summary(mentalhealth_2016_df$age)

mentalhealth_2016_df %>% 
  ggplot(aes(x = age)) +
  geom_density()
```

```{r}
mentalhealth_2016_tidied =
  mentalhealth_2016_df %>% 
  filter(age < 100) %>% 
  mutate(gender = str_replace(gender, "^[Ww]oman$", "Female"),     # female
         gender = str_replace(gender, "^[Ff]$", "Female"),
         gender = str_replace(gender, "^fem$", "Female"),
         gender = str_replace(gender, "^female$", "Female"),
         gender = str_replace(gender, "^female/woman$", "Female"),
         gender = str_replace(gender, "^fm$", "Female"),
         gender = str_replace(gender, "AFAB", "Female"),
         #gender = str_replace(gender, "AFAB", "Female"),
         gender = str_replace(gender, "^[Mm]$", "Male"),  # male
         gender = str_replace(gender, "^mail$", "Male"),  #?
         gender = str_replace(gender, "^MALE$", "Male"),
         gender = str_replace(gender, "^Male.$", "Male"),
         gender = str_replace(gender, "^Malr$", "Male"),    #?
         gender = str_replace(gender, "^[Mm]an$", "Male"),
         #gender = str_replace(gender, "^man$", "Male"),
         gender = str_replace(gender, "^male$", "Male"))

#summary(as.factor(mentalhealth_2016_df$gender))
#summary(mentalhealth_2016_df$age)   # need filter 99 or not?

head(mentalhealth_2016_df)
```

```{r}
mentalh_vs_physical =
  mentalhealth_2016_df %>% 
  #filter(tech_company != 0 | tech_role != 0) 
  #select(num_employees, tech_company, tech_role, benefits, )
  select(contains("mental"), contains("physical")) %>% 
  select(- contains("previous"))


```

```{r}
mentalhealth_2016_tidied %>% 
  ggplot(aes(x = num_employees)) +
  geom_bar(aes(fill = mental_health_now))
```

```{r}
mental_data_fit = 
  mentalhealth_2016_tidied %>%
  mutate(tech = ifelse(tech_company == 1 | tech_role == 1, 1, 0)) %>%
  filter(mental_health_now != "Maybe") %>% 
  filter(gender == "Male" | gender == "Female") %>% 
  filter(!is.na(num_employees) & !is.na(tech) & !is.na(family_history) & !is.na(mental_health_previous) & !is.na(age) & !is.na(gender) & !is.na(work_remotely) & !is.na(mental_health_now)) %>%
  mutate(num_employees = as.factor(num_employees), 
         tech_company = as.factor(tech_company), 
         tech_role = as.factor(tech_role), 
         family_history = as.factor(family_history), 
         mental_health_previous = as.factor(mental_health_previous), 
         gender = as.factor(gender), 
         work_remotely = as.factor(work_remotely), 
         mental_health_now = as.factor(mental_health_now)) %>%
  select(mental_health_now, num_employees, tech, family_history, mental_health_previous, age, gender, work_remotely)

glm_stats = glm(mental_health_now ~ ., data = mental_data_fit, family = binomial()) %>% 
  broom::tidy()

```
