---
title: "report_model"
author: "Xinyi Lin"
date: "12/5/2018"
output: html_document
---

```{r, message = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
```

# Import and tidy data

First, we should have a roughly understanding about this data.

```{r, message = FALSE, warning = FALSE}
mentalhealth_2016_df = read_csv("./data/mental_health_in_tech_2016.csv") 
```

```{r}
colnames(mentalhealth_2016_df) <- c("self_employed", "num_employees", "tech_company", "tech_role", "benefits", "care_options", "employer_discussion", "employer_help", "anonymity", "medical_leave", "mental_health_consequences", "physical_health_consequences", "coworkers_discussion", "supervisor_discussion", "mental_vs_physical", "obs_consequence", "medical_coverage", "help_resourcces", "whether_reveal_business_contacts", "reveal_concequences_business_contects", "whether_reveal_coworkers", "reveal_concequences_coworkers", "productivity_affect", "work_time_affected", "preemployers", "preemployers_benefits", "preemployers_care_options", "preemployers_discussion", "preemployer_help", "pre_anonymity", "pre_mental_health_consequences", "pre_physical_health_consequences", "pre_coworkers_discussion", "pre_supervisors_discussion", "pre_mental_vs_physical", "pre_obs_consequence", "physical_health_interview", "physical_health_interview_reason", "mental_health_interview", "mental_health_interview_reason", "career_influence", "coworkers_view", "friends_family_share", "unsupportive_badly_handled", "less_likely_reveal", "family_history", "mental_health_previous", "mental_health_now", "condition_diagnosed", "possible_condition", "professional_diagnosed", "condition_professional_diagnosed", "seek_treatment", "work_interferes_treated", "work_interferes_untreated", "age", "gender", "country_live", "territory_live", "country_work", "territory_work", "work_position_kind", "work_remotely")
```

```{r}
mentalhealth_2016_tidied =
  mentalhealth_2016_df %>% 
  filter(age < 100) %>% 
  mutate(gender = str_replace(gender, "^[Ww]oman$", "Female"),     # female
         gender = str_replace(gender, "^[Ff]$", "Female"),
         gender = str_replace(gender, "^fem$", "Female"),
         gender = str_replace(gender, "^female$", "Female"),
         gender = str_replace(gender, "^female/woman$", "Female"),
         gender = str_replace(gender, "^fm$", "Female"),
         gender = str_replace(gender, "AFAB", "Female"),
         #gender = str_replace(gender, "AFAB", "Female"),
         gender = str_replace(gender, "^[Mm]$", "Male"),  # male
         gender = str_replace(gender, "^mail$", "Male"),  #?
         gender = str_replace(gender, "^MALE$", "Male"),
         gender = str_replace(gender, "^Male.$", "Male"),
         gender = str_replace(gender, "^Malr$", "Male"),    #?
         gender = str_replace(gender, "^[Mm]an$", "Male"),
         #gender = str_replace(gender, "^man$", "Male"),
         gender = str_replace(gender, "^male$", "Male"))
```

# model building

We tried to build a model shows possible factors which might cause mental health disorder. First, we exclude variables which describe influence of mental health disorders or benefits about mental health disorders. Besides, `mental_health_now` of most experiement subjects equals to `mental_health_previous`, which means collinearity among these two variables is high. So we also exclude `mental_health_previous` to prevent it from highly influencing results. After that, we defined experiement subjects have tech-related job when he or she works in tech-company or has tech-related jobs.

Variables left include `mental_health_now` which is our interested variable and possible factors `num_employees`, `tech`, `family_history`, `age`, `gender`, `work_remotely`.

```{r}
mental_data_fit = 
  mentalhealth_2016_tidied %>%
  mutate(tech = ifelse(tech_company == 1 | tech_role == 1, 1, 0)) %>%
  filter(mental_health_now != "Maybe") %>% 
  filter(gender == "Male" | gender == "Female") %>% 
  filter(!is.na(num_employees) & !is.na(tech) & !is.na(family_history) & !is.na(mental_health_previous) & !is.na(age) & !is.na(gender) & !is.na(work_remotely) & !is.na(mental_health_now)) %>%
  mutate(num_employees = as.factor(num_employees), 
         tech_company = as.factor(tech_company), 
         tech_role = as.factor(tech_role), 
         family_history = as.factor(family_history), 
         mental_health_previous = as.factor(mental_health_previous), 
         gender = as.factor(gender), 
         work_remotely = as.factor(work_remotely), 
         mental_health_now = as.factor(mental_health_now)) %>%
  #select(mental_health_now, num_employees, tech, family_history, mental_health_previous, age, gender, work_remotely)    # add `mental_health_previous
  select(mental_health_now, num_employees, tech, family_history, age, gender, work_remotely)
```

Since all possible factors except for `age` are categorical variables, using linear regression might cause too much interaction, so we use conditional inference tree and decision tree to build our model.

## using conditional inference tree

First, we seperate original data to train data and test data.

```{r, message = FALSE}
library(party)

set.seed(3)

index <- sample(2,nrow(mental_data_fit),replace = TRUE,prob = c(0.7,0.3))
traindata <- mental_data_fit[index == 1,]
testdata <- mental_data_fit[index == 2,]
```

Then, we use train data to build model.

```{r}
fitted_ctree <- ctree(mental_health_now ~ ., data = traindata)
plot(fitted_ctree, main = "Conditional Inference Tree")
```

Conditional inference tree is built based on information measures, so those which give more information about response are shown first. According to the result, family history has huge influence in mental health disorders followed by gender and number of employees in the working company in different branches.

Finally, we use test data to test model

```{r}
ctree.pred <- predict(fitted_ctree, testdata, type = "response")
table(testdata$mental_health_now, ctree.pred, 
                    dnn = c("Actual", "Predicted"))

library(caret)

confusionMatrix(table(ctree.pred,testdata$mental_health_now))

ctree_term = confusionMatrix(table(ctree.pred,testdata$mental_health_now)) %>% 
  broom::tidy() %>% 
  filter(term == "sensitivity" | term == "specificity") %>% 
  select(term, estimate) %>% 
  rename(ctree_estimate = estimate)
```

We use cross-validation to do further test.

```{r}
cv_df =
  crossv_mc(mental_data_fit, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

tree_term = function(tree_pred, test) {
  confusionMatrix(table(tree_pred,test$mental_health_now)) %>% 
  broom::tidy() %>% 
  filter(term == "sensitivity" | term == "specificity") %>% 
  select(term, estimate)}

ctree_cv_df = 
  cv_df %>% 
  mutate(ctree_mod  = map(train, ~ctree(mental_health_now ~ ., data = .x))) %>% 
  mutate(ctree_pred = map2(ctree_mod, test, ~predict(.x, .y, type = "response")),
         tree_term = map2(ctree_pred, test, ~tree_term(tree_pred = .x, test = .y))) %>% 
  unnest(tree_term) %>% 
  group_by(term) %>% 
  summarise(mean = mean(estimate)) %>% 
  rename(ctree_mean = mean)

ctree_cv_df
```

## using decision tree

First, we seperate original data to train data and test data.

```{r}
library(rpart)
library(rpart.plot)

set.seed(13)
 
index <- sample(2,nrow(mental_data_fit),replace = TRUE,prob = c(0.7,0.3))
traindata <- mental_data_fit[index == 1,]
testdata <- mental_data_fit[index == 2,]
```

Then, we use train data to build model.

```{r}
fitted_dtree <- rpart(formula = mental_health_now ~ ., data = traindata, method = 'class')

rpart.plot(fitted_dtree)
```

Decision inference tree is built based on significant level, so those which are more significant are shown first. According to the result, family history also has huge influence in mental health disorders and is followed by number of employees in the working company in different branches when experimental subject didn't know their family history.

Finally, we use test data to test model

```{r}
dtree_pred <- predict(object = fitted_dtree,newdata = testdata,type = 'class')
table(dtree_pred, testdata$mental_health_now)

confusionMatrix(table(dtree_pred,testdata$mental_health_now))

dtree_term = confusionMatrix(table(dtree_pred,testdata$mental_health_now)) %>% 
  broom::tidy() %>% 
  filter(term == "sensitivity" | term == "specificity") %>% 
  select(term, estimate) %>% 
  rename(dtree_estimate = estimate)
```

We use cross-validation to do further test.

```{r}
cv_df =
  crossv_mc(mental_data_fit, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

dtree_cv_df = 
  cv_df %>% 
  mutate(dtree_mod  = map(train, ~rpart(formula = mental_health_now ~ ., data = .x, method = 'class'))) %>% 
  mutate(dtree_pred = map2(dtree_mod, test, ~predict(.x, .y, type = "class")),
         tree_term = map2(dtree_pred, test, ~tree_term(tree_pred = .x, test = .y))) %>% 
  unnest(tree_term) %>% 
  group_by(term) %>% 
  summarise(mean = mean(estimate)) %>% 
  rename(dtree_mean = mean)

dtree_cv_df
```

```{r}
inner_join(ctree_cv_df, dtree_cv_df)
```

Comparing cross-validation results of conditional inference tree and decision tree, two models have similar sensitivity and specificity and both sensitivity are smaller than specificity. 

